Finch: A Datastructure-Driven Array Programming Language

### 2024-03-15 main.tex
appears fixed

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{array}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

@@

@@

\section{The Tensor Interface}

\subsection{Tensor Lifecycle, Declare, Freeze, Thaw, Unfurl}

\subsection{Level Abstraction}

\begin{enumerate}
\item fibers
\item assembly
\item reassembly
\end{enumerate}

\subsection{Core Level Langage Primitives}
\begin{enumerate}
\item SparseList
\item SparseDict
\item ...
\end{enumerate}

\section{The Finch High-Level API (Needs a Name)}

\subsection{Finch Logic}

\subsection{Finch Interpreter}

\subsection{Lowering}
\subsubsection{Heuristic Optimization}

@@

\subsubsection{High-level kernel fusion}
Find an example where fusing the python interface gives a big speedup over non-fused kernels.

>>>>

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
%\usepackage{amssymb}
\usepackage{array}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\newcommand\teo[1]{\textcolor{red}{teo:#1}}

@@

\section{Bridging Looplets and Finch: The Tensor Interface}
\teo{I am doing stuff in this section.}
\input{sections/tensors.tex}

@@

@@

\subsection{Implementing Numpy Array API in Finch}
\subsubsection{The Finch High-Level API (Needs a Name)}

\subsubsection{Finch Logic}

\subsubsection{Finch Interpreter}

\subsubsection{Lowering}
\subsubsection{Heuristic Optimization}

Find an example where fusing the python interface gives a big speedup over non-fused kernels.

%matmul, mttkrp, repeated ttm, triangle counting, multiple pointwise,
%in-place.
%dot((v^t .* u), w)) vs. 
%(v^t .* dot(u, w))
